---
title: "Question 2"
author: "Saurabh Malkar"
date: "October 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 here we create transactions dataframe and convert unix timestamp to standard date formate. and get the summary of the table . We also remove the outtliers.
```{r}
networktenx<-read.table(file="networktenxpayTX.txt",header=F,sep=" ")
networktenx <- networktenx[ which(networktenx$V4<=2.05218256e+26), ]
colnames(networktenx)<-c("FromId","ToId","date","TotalAmount")
summary(networktenx)

networktenx$date<- as.Date(as.POSIXct(networktenx$date, origin="1970-01-01"))
```

here we are taking the opening value of the token as the Price of that day.

```{r}
pricetenx<-read.table(file="tenxpay.txt",header=T,sep="\t")
summary(pricetenx)

pricetenx<-pricetenx[c(1,2)]
pricetenx$Date<-as.Date(pricetenx$Date,format="%m/%d/%Y")
colnames(pricetenx)<-c("Date","Price")
```

Splitting the main transaction table into 7 Layers based on the amount of transactions. The layer size is not fixed as the all the interval of amount of transaction do not contain equal number of transaction . Equally splitted layers may contain very less feature to measure the required correlation.
the layer are splitted into from $$1 \:to \:10^3 \: ,10^3 \: to \: 10^{10} \:, 10^{10}\: to \:10^{15}\:, 10^{15}\: to \:10^{18}\: , 10^{18}\: to \:10^{20}\:, 10^{20} \: to \:10^{24}\: and \:10^{24}\: and \:above\: are\: layer\: 7\:,\:6,\:5,\:4,\:3,\:2,\:1 \:respectively.$$

```{r}
layer_1<-networktenx[which(networktenx$TotalAmount>=1e+24),]
layer_2<-networktenx[which(networktenx$TotalAmount>=1e+20 & networktenx$TotalAmount< 1e+24 ),]
summary(layer_2)

layer_3<-networktenx[which(networktenx$TotalAmount>=1e+18 & networktenx$TotalAmount< 1e+20 ),]
layer_4<-networktenx[which(networktenx$TotalAmount>=1e+15 & networktenx$TotalAmount< 1e+18 ),]
layer_5<-networktenx[which(networktenx$TotalAmount>=1e+10 & networktenx$TotalAmount< 1e+15 ),]
layer_6<-networktenx[which(networktenx$TotalAmount>=1e+3 & networktenx$TotalAmount< 1e+10 ),]
layer_7<-networktenx[which(networktenx$TotalAmount>=1e+0 & networktenx$TotalAmount< 1e+3),]
```
Here we are calculating the number of transaction that happened on a particular date by calculating the frequency of the date.

```{r}
Flayer_1 <-c(layer_1[,3])
summary(Flayer_1)
count_layer1<-as.data.frame(table(Flayer_1))
colnames(count_layer1)<-c("Date","Frequency")
nrow(count_layer1)
```

```{r}
library(anytime)
count_layer1$Date<- anydate(count_layer1$Date)
```


joining the price table and transaction frequency table using date as the key.
```{r}
library(sqldf)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer1 f INNER JOIN pricetenx p WHERE f.Date=p.Date")
df3
```

here we are finding the correlation of the price and the number of transaction that happened on the date. 

For the First layer i.e. transaction amount greater that $$10^{24}$$ we get a correlation of 0.83 this shows that large nummber of transactions happened at higher price where each transaction involves more that $$10^{24}$$ tokens. 
```{r}
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")
```
```{r}
library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


Finding correlation For layer two. It found out to be 0.018 that is not much correlation between price and number of transactions with amount between $$10^{20}\: to\: 10^{24}$$. Similar steps are done to following layers.
```{r}
Flayer <-c(layer_2[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```

```{r}
Flayer <-c(layer_3[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```
```{r}
Flayer <-c(layer_4[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```
This layer has a negative correlation that means as the price increases the number of transactions are decreased.
```{r}
Flayer <-c(layer_5[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```

```{r}
Flayer <-c(layer_6[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```
```{r}
Flayer <-c(layer_7[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


We take low as the price of that day for all the 7 layers. And after calculating the pearson correlation that all the layer except layer 7 has a significant negative correlation hence we can conclude that as the price increases the number of transactions decreases.

```{r}
pricetenx<-read.table(file="tenxpay.txt",header=T,sep="\t")
summary(pricetenx)

pricetenx<-pricetenx[c(1,4)]
pricetenx$Date<-as.Date(pricetenx$Date,format="%m/%d/%Y")
colnames(pricetenx)<-c("Date","Price")

```
```{r}
Flayer_1 <-c(layer_1[,3])
summary(Flayer_1)
count_layer1<-as.data.frame(table(Flayer_1))
colnames(count_layer1)<-c("Date","Frequency")
nrow(count_layer1)
```

```{r}
library(anytime)
count_layer1$Date<- anydate(count_layer1$Date)
```
```{r}
library(sqldf)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer1 f INNER JOIN pricetenx p WHERE f.Date=p.Date")
```
```{r}
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")
```
```{r}
library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```
For layer two
```{r}
Flayer <-c(layer_2[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


```{r}
Flayer <-c(layer_3[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


```{r}
Flayer <-c(layer_4[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```



```{r}
Flayer <-c(layer_5[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


```{r}
Flayer <-c(layer_6[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```

```{r}
Flayer <-c(layer_7[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "pearson")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```


Trying kendall correlation on layer 1 with low as the price of the day. The correlation we get is worst than pearson which was -0.33
```{r}
Flayer <-c(layer_1[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "kendall")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```

Trying spearman correlation on layer 1 with low as the price of the day. The correlation we get is worst than pearson which was -0.33
```{r}
Flayer <-c(layer_1[,3])
summary(Flayer)
count_layer<-as.data.frame(table(Flayer))
colnames(count_layer)<-c("Date","Frequency")
nrow(count_layer)

count_layer$Date<- anydate(count_layer$Date)
df3<-sqldf("SELECT f.Date, p.Price, f.Frequency FROM count_layer f INNER JOIN pricetenx p WHERE f.Date=p.Date")
cor.test(df3$Price, df3$Frequency, 
                    method = "spearman")

library("ggpubr")
ggscatter(df3, x = "Price", y = "Frequency", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "Open Price", ylab = "Frequency of Token Amount")
```